### 2008-05-16 trunk/Papers/dl-gre-08/related.tex

Perhaps closest in spirit to our approach is Krahmer et al.\ graph
algorithm~\shortcite{Krahmer2003}, which also computes REs by
extending them successively.  However, their subgraphs go beyond the
expressive power of \alc\ in that they can distinguish between ``the
dog that bites a dog'' and ``the dog that bites itself''.  The price
they pay for this increase in expressive power is an NP-complete
worst-case complexity.  Interestingly, Krahmer et al.\ themselves
discuss the possibility of seeing their subgraphs as formulas of
hybrid logic which are satisfied at the points where the subgraph can
be embedded; and hybrid logics can be seen as very expressive
description logics \cite{arec:hybr05b}.

>>>>

Perhaps closest in spirit to our approach is Krahmer et al.'s graph
algorithm~\shortcite{Krahmer2003}, which also computes REs by
extending them successively.  However, their subgraphs go beyond the
expressive power of \alc\ in that they can distinguish between ``the
dog that bites a dog'' and ``the dog that bites itself''.  The price
they pay for this increase in expressive power is an NP-complete
worst-case complexity.  Interestingly, Krahmer et al.\ themselves
discuss the possibility of seeing their subgraphs as formulas of
hybrid logic which are satisfied at the points where the subgraph can
be embedded; and hybrid logics can be seen as very expressive
description logics \cite{arec:hybr05b}.
